Excuse me, do you have a moment to talk about version control?

### 2017-05-19 README.Rmd
I. HAVE. MADE. A. BIBLIOGRAPHY. 🔥
Make both formats play nice re: bibliography

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: |
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton and Colin Rundel.
blinded: 0
output:
  rticles::asa_article: null
  github_document:
    toc: yes
keywords: version control
abstract: Abstract abstract abstract.
---

@@

Transparency about process and product is increasingly important in science. The SOMETHING for reproducibility is well accepted. A more underappreciated benefit is democratization of our field, as this affords a much broader audience a clear view of how scientists and programmers work.

@@

>>>>

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: |
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton and Colin Rundel.
blinded: 0
output:
  rticles::asa_article: null
  github_document:
    toc: yes
keywords: version control
abstract: Abstract abstract abstract.
bibliography: git-github-for-stats.bib
---

@@

Transparency about [@greenwade93] process and product is increasingly important in science. The SOMETHING for reproducibility is well accepted. A more underappreciated benefit is democratization of our field, as this affords a much broader audience a clear view of how scientists and programmers work.

@@

```{r eval = is_github_document, echo = FALSE, results = 'asis'}
## surely there is a better way?
cat("## References\n")
```
